PANCHANGE_data_preprocessing

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Checked COPING PHQ chunks

Calculate sum score for PCL-6 base
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores

@@

```{r}
coping.glad.phq.raw %>%
  select(contains("little")) %>%
  colnames
```

>>>>

Calculate sum score for PCL-6 base
The sum scores here will not be accurate if we are using complete cases. Only use sum scores here for complete cases, otherwise the minimum will be 0 where it should be 6. 
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores

@@

```{r select phq little}
coping.glad.phq.raw %>%
  select(contains("little")) %>%
  colnames
```
